### 2022-06-01 LaTeX/report.tex
Updates

The following case, \textit{i.e.} $w \in \texttt{visited }e$ is much more complicated. In this case, $e' = \texttt{dfs}~v~e$. Altgouh the proof remains straightforward, the different properties are more difficult to establish. The main idea is to use the fact that $\texttt{post\_dfs}~w~e~e'$ is satisfied to show the pre-condition : $\texttt{pre\_dfss}~v~vs-\{w\}~e$. From the assumptions, we can obtain the post-condition : $\texttt{post\_dfss}~v~vs-\{w\}~e~e'$. There still remains some work to do inorder to show that this implies the final post-condition, \textit{i.e.} that $\texttt{post\_dfss}~v~vs-\{w\}~e~(\texttt{dfss}~v~vs-\{w\}~e)$ is satisfied.

@@

\section{Conclusion}

\ednote{sm}{Don't forget to write a conclusion, explaining what has been done, what is missing / could be improved, and what your experience has been.}

>>>>

The following case, \textit{i.e.} $w \in \texttt{visited }e$ is much more complicated. In this case, $e' = \texttt{dfs}~v~e$. Although the proof remains straightforward, the different properties are more difficult to establish. The main idea is to use the fact that $\texttt{post\_dfs}~w~e~e'$ is satisfied to show the pre-condition : $\texttt{pre\_dfss}~v~vs-\{w\}~e$. From the assumptions, we can obtain the post-condition : $\texttt{post\_dfss}~v~vs-\{w\}~e~e'$. There still remains some work to do inorder to show that this implies the final post-condition, \textit{i.e.} that $\texttt{post\_dfss}~v~vs-\{w\}~e~(\texttt{dfss}~v~vs-\{w\}~e)$ is satisfied.

@@

\section{Conclusion}
\subsection{What has been done ?}
The proof of correctness is almost done. The model and the invariants we have come up with are quite comprehensive and coherent now. We regularly test newer invariants with TLC, a model checker for specifications written in TLA+. Thus, we also have a TLA+ version of this algorithm, although it is not really the same implementation. However, as we juste use it to verify a few properties on specific examples, it is just meant to give us a better feeling of confidence or find counter examples. I've been working on this project for almost a year, and yet it's only been a month or two that I really feel like I understand the algorithm.

\subsection{What is missing ?}
In the proof of correctness, some intermediate proofs are still skipped. It is mainly due to some former invariants that were deleted because they were wrong.

Another important missing piece is the proof of termination of the functions. In order to achieve this, we need to define a measure and find a quantity that strictly decreases for that measure. In \texttt{sub\_env}, the inclusions are not strict. An idea would be to consider the complementary set of visited between two calls of \texttt{dfs} as a set getting strictly smaller.

\subsection{My experience}
Before starting the project, I had no knowledge of formal methods. I had to learn it quickly in one month and as I went along. I liked it right away. As I am very attached to rigour, there is a very addictive side to wanting to demonstrate everything. This is why I decided to pursue my career in the field of formal methods.
\BlankLine
It was also my first experience in the world of research. It was an opportunity to confirm my desire to do basic research, and I also found a domain. I was also able to meet several of the researchers of the \href{https://www.loria.fr/fr/la-recherche/les-equipes/mosel-veridis/}{MOSEL-VERIDIS} team at \href{https://www.loria.fr/en/}{LORIA} in Nancy, as well as \href{https://cs.au.dk/~jaco/}{Jaco Van de Pol} who is the supervised the thesis of Vincent Bloemen \cite{bloemen_strong_2019}.
